---
title: "Hsieh_master"
author: "Pei Yang Hsieh"
date: 2018-09-28
output: html_document
---

## Load libraries

```{r setup, include=FALSE}
library(tidyverse)
library(readxl) #read excel
library(haven) #read SAS, Stata, SPSS
```

## Outputs

output:
  html_document:
    toc: true
    toc_float: true
    
output:
  pdf_document: default
  
output:
  word_document: default

## Formatting

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header

Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell 



'eval = FALSE' : code will be displayed but not executed; results are not included.

'echo = FALSE' : code will be executed but not displayed; results are included.

'include = FALSE' : code will be executed but not displayed; results are not included.

'message = FALSE' and 'warning = FALSE' : prevents messages and warnings from being displayed.

'results = hide' and 'fig.show = hide' : prevents results and figures from being shown, respectively.

'collapse = TRUE' : output will be collapsed into a single block at shown at the end of the chunk.

'error' : errors in code will stop rendering when FALSE; errors in code will be printed in the doc when TRUE. The default is FALSE and you should almost never change it.

## Building Blocks

```{r building_blocks, eval = FALSE}

#Create random uniform distribution
x = runif(20)
x
mean(x)
var(x)

#Data frame of random sample

example_df = tibble(
  vec_numeric = 5:8,
  vec_char = c("My", "name", "is", "Jeff"),
  vec_logical = c(TRUE, TRUE, TRUE, FALSE),
  vec_factor = factor(c("male", "male", "female", "female"))
)

class(example_df$vec_numeric)
```

## Data Import

```{r import, eval = FALSE}

getwd()

litters_data = read_csv(file = "./data/FAS_litters.csv")

names(litters_data)

litters_data = janitor::clean_names(litters_data)
names(litters_data)

skimr::skim(litters_data)

'col_names' : usually TRUE. If FALSE, column names are X1, X1, … . You can also supply column names.

'na' : string vector containing character expressions for missing values.

'skip' : number of rows to skip before reading data.

litters_data = read_csv(file = "./data/FAS_litters.csv",
  col_types = cols(
    Group = col_character(),
    `Litter Number` = col_character(),
    `GD0 weight` = col_double(),
    `GD12 weight` = col_double(),
    `GD of Birth` = col_integer(),
    `Pups born alive` = col_integer(),
    `Pups dead @ birth` = col_integer(),
    `Pups survive` = col_integer()
  )
)

litters_data = read_csv(file = "./data/FAS_litters.csv",
  col_types = "ccddiiii"
)

mlb11_data = read_excel("data/mlb11.xlsx", n_max = 20)
head(mlb11_data, 5)

pulse_data = read_sas("./data/public_pulse_data.sas7bdat")
head(pulse_data, 5)

```



## Data Manipulation

###Select

```{r select, eval = FALSE}

#specify columns you want by naming all of them
select(litters_data, group, litter_number, gd0_weight, pups_born_alive)

#specify range of columns to keep
select(litters_data, group:gd_of_birth)

#specify columns to remove
select(litters_data, -pups_survive)

#rename variables
rename(litters_data, GROUP = group, LiTtEr_NuMbEr = litter_number)

#reorganize columns 
select(litters_data, litter_number, group, everything())

In larger datasets, I also use starts_with(), ends_with(), and contains() often.

```

### Filter

```{r filter, eval = FALSE}

gd_of_birth == 20

pups_born_alive >= 2

pups_survive != 4

!(pups_survive == 4)

group %in% c("Con7", "Con8")

group == "Con7" & gd_of_birth == 20

!is.na(wt_increase)

filter(pups_data, sex == 1)

filter(pups_data, sex == 2, pd_walk < 11)

```

### Mutate

```{r mutate, eval = FALSE}

mutate(litters_data,
  wt_gain = gd18_weight - gd0_weight,
  group = tolower(group)
)

#Create a variable that subtracts 7 from PD pivot
mutate(pups_data, pivot_minus7 = pd_pivot - 7)

#Create a variable that is the sum of all the PD variables
mutate(pups_data, pd_sum = pd_ears + pd_eyes + pd_pivot + pd_walk)
```

### Arrange

```{r arrange, eval = FALSE}

head(arrange(litters_data, group, pups_born_alive), 10)

```

### Piping

```{r pipe, eval = FALSE}

litters_data = 
  read_csv("./data/FAS_litters.csv", col_types = "ccddiiii") %>%
  janitor::clean_names() %>%
  select(-pups_survive) %>%
  mutate(
    wt_gain = gd18_weight - gd0_weight,
    group = tolower(group))


read_csv("./data/FAS_pups.csv", col_types = "ciiiii") %>%
  janitor::clean_names() %>% 
  filter(sex == 1) %>% 
  select(-pd_ears) %>% 
  mutate(pd_pivot_gt7 = pd_pivot > 7
```


## Plotting

```{r plot, eval = FALSE}

set.seed(1)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)

#histogram
ggplot(plot_df, aes(x = x)) + geom_histogram()

#scatterplot of x and y
ggplot(plot_df, aes(x = x, y = y)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```


