---
title: "Hsieh_master"
author: "Pei Yang Hsieh"
date: 2018-09-28
output: html_document
---

## Load libraries

```{r setup, include=FALSE}
library(tidyverse)
```

## Outputs

output:
  html_document:
    toc: true
    toc_float: true
    
output:
  pdf_document: default
  
output:
  word_document: default

## Formatting

Text formatting 
------------------------------------------------------------

*italic*  or  _italic_
**bold**  or  __bold__
`code`
superscript^2^ and subscript~2~


Headings
------------------------------------------------------------

# 1st Level Header

## 2nd Level Header

### 3rd Level Header

Lists
------------------------------------------------------------

*   Bulleted list item 1

*   Item 2

    * Item 2a

    * Item 2b

1.  Numbered list item 1

1.  Item 2. The numbers are incremented automatically in the output.


Tables 
------------------------------------------------------------

First Header  | Second Header
------------- | -------------
Content Cell  | Content Cell
Content Cell  | Content Cell 



'eval = FALSE' : code will be displayed but not executed; results are not included.

'echo = FALSE' : code will be executed but not displayed; results are included.

'include = FALSE' : code will be executed but not displayed; results are not included.

'message = FALSE' and 'warning = FALSE' : prevents messages and warnings from being displayed.

'results = hide' and 'fig.show = hide' : prevents results and figures from being shown, respectively.

'collapse = TRUE' : output will be collapsed into a single block at shown at the end of the chunk.

'error' : errors in code will stop rendering when FALSE; errors in code will be printed in the doc when TRUE. The default is FALSE and you should almost never change it.

## Building Blocks

```{r building_blocks}

#Create random uniform distribution
x = runif(20)
x
mean(x)
var(x)

#Data frame of random sample

example_df = tibble(
  vec_numeric = 5:8,
  vec_char = c("My", "name", "is", "Jeff"),
  vec_logical = c(TRUE, TRUE, TRUE, FALSE),
  vec_factor = factor(c("male", "male", "female", "female"))
)

class(example_df$vec_numeric)
```

## Plotting

```{r plot}

set.seed(1)

plot_df = tibble(
  x = rnorm(1000, sd = .5),
  y = 1 + 2 * x + rnorm(1000)
)

#histogram
ggplot(plot_df, aes(x = x)) + geom_histogram()

#scatterplot of x and y
ggplot(plot_df, aes(x = x, y = y)) + geom_point()

ggsave("scatter_plot.pdf", height = 4, width = 6)
```

